%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Member Technical} % Job title
    {Broadridge Financial Solutions} % Organization
    {Hyderabad India} % Location
    {Jun. 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Spearheaded the creation, maintenance, and enhancement of Kubernetes clusters on Cloud as well as on Prem.}
        \item {Developed Terraform codebase for infrastructure provisioning, streamlining deployment processes and improving efficiency.}
        \item {Contributed to the feature additions of CLI and Web UI internal applications, enhancing functionality and user experience for the team.}
        \item {Managed the creation and maintenance of Terraform modules, promoting code reuse and standardization across projects.}
        \item {Engineered an SDK in Golang for CloudHealth monitoring tool, facilitating seamless integration and efficient monitoring of cloud resources.}
        \item {Designed and implemented a Terraform provider for CloudHealth Monitoring tool, enabling automated provisioning and configuration management.}
        \item {Implemented multiple automations deployed as Lambda functions using Jenkins and Terraform, reducing manual intervention and enhancing workflow efficiency.}
        \item {Collaborated on the development of a tool for automating development and deployment on Kubernetes for application teams, improving deployment processes and accelerating delivery cycles.}
        \item {Provided support to application teams in containerizing their applications and hosting them on Kubernetes platforms, ensuring compatibility and reliability.}
        \item {Mentored interns and provided knowledge transfer sessions to team members on relevant technologies and best practices.}
        \item {Presented tools and solutions developed, showcasing their value and potential impact on team productivity.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Contract Associate / Intern} % Job title
    {Broadridge Financial Solutions} % Organization
    {Hyderabad, India} % Location
    {Sep. 2022 - Jun. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained and enhanced internal web applications, incorporating new features and ensuring smooth hosting operations.}
        \item {Contributed to the upkeep and enhancement of internal CLI tools, streamlining processes and boosting operational efficiency.}
        \item {Conducted research and proof-of-concept studies to identify optimal methods for cost optimization on cloud platforms.}
        \item {Implemented best practices, both manually and through automation, to achieve cost optimization targets effectively.}
        \item {Played a role in maintaining and upgrading containerized applications for internal use, ensuring reliability and scalability.}
        \item {Developed and deployed AWS Lambda code to automate manual processes, significantly reducing operational overhead and enhancing efficiency.}
        \item {Gained practical experience in software development, cloud optimization, and containerization, translating theoretical knowledge into real-world applications.}
        \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
