%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Position of Responsibility}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry    
    {ACM SOA Students Chapter} % Organization/group
    {Treasurer} % Affiliation/role
    {Bhubaneswar, India} % Location
    {Sep. 2021 - Sep. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Managed ACM student chapter budget effectively, ensuring optimal fund allocation for events.}
        \item {Implemented streamlined reimbursement processes and maintained meticulous financial records.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {BloodUnite} % Organization/group
    {Human Resource Manager} % Affiliation/role
    {Bhubaneswar, India} % Location
    {Aug. 2021 - Nov. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Led recruitment drives to build a dedicated volunteer base, fostering team engagement and cohesion at Bloodunite.}
        \item {Implemented tailored HR policies promoting team engagement.}
        \item {Established a supportive work environment, ensuring employees are motivated and committed to the organization's noble cause.}
        \item {Orchestrated effective blood fulfillment initiatives, leveraging team cohesion and engagement for community impact.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {The Rising Youth~~~·~~~Grasp Anything} % Organization/group
    {State Head of Maharashtra} % Affiliation/role
    {Remote} % Location
    {Jan. 2021 - Apr. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Mentored a diverse team of student journalists, fostering journalistic integrity and amplifying youth voices in Maharashtra.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\end{cventries}
